Dynamic capabilities and competitive advantage

### 2019-09-21 article4_tommylars.tex
before cleanup and writeup

\documentclass[review,fleqn]{elsarticle}
\usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
\usepackage{subfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{filecontents}
\input{preamble.tex}
%%\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\setlength{\mathindent}{0pt} %% NB MAYBEREMOVE BEFORE SUBMISSION

%%%% TURN OFF PAGE NUMBER FOR INCLUSION IN THESIS
%\pagenumbering{gobble}
%%%%%%%

\begin{document}

@@

\title{Evolution of (dynamic) capabilities and its performance implications: An empirical test and extension}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

To test the relationships between dynamic capabilities and competitive advantage we need a
proper metric of both. We also benefit vastly from studying the same firms over time.  The
lack of h longitudinal studies to investigate dynamics over time and control for path
dependency of organizational routines has been noted as permanent limitation for moving
the DC literature forward empirically and theoretically \cite{Schilke2018}. To remedy this
gap in the literature and to investigate the empirical characteristics of the Zollo \&
Winter model we sampled a subset of Norwegian technology firms ($N=241$) over two time
periods.

@@

All firms that registered R\&D activities during May to December 2005 were approached
totaling in all 1721 firms. A web-based questionnaire was developed containing the
measures of the key constructs of this paper. A link to the questionnaire was e-mailed to
the firms within a month after they registered R\&D activities. The initial mailing was
followed by two e-mail reminders. Of the firms approached, 1199 (70 \%) returned filled-in
questionnaires. The 1199 companies that filled out the questionnaire were contacted again
9 years later. The majority of firms were contacted in spring/summer 2014. All received a
web-based questionnaire containing the same measures of DC, CA, OR and so on. 283 of the
firms returned filled-in questionnaire.

@@

To control for survivor and non-response among our firms over time due to exogenous
factors such as exit, bankruptcy and so on, we estimate a model Heckman correction (Hair,
2010). Applied to the context of this paper, Heckman regression is a method that in the
first step analyses the probability that a firm at $T_1$ will answer the survey at $T_2$
depending on observables at $T_1$. This is modeled as a probit regression. Based on the
probit regression in $T_1$, the inverse Mills ratio (sometimes called lambda) is added to the
analysis in the second step where the goal is to analyze the relationship between our
focal constructs (using regular OLS regression). The inverse Mills ratio is a control
factor which controls for unobserved heterogeneity. More concretely, the inverse Mills
ratio will control for unobserved factors that are related to both firms’ probability of
answering the survey at $T_2$ (ref).

@@

The focal constructs of this paper are deliberate learning, dynamic capabilities,
operational routines and competitive advantage. These are all operationalized using the
survey data described above. Table 1 below describes the items used to operationalize the
focal constructs and their internal validity in forming an additive index (Cronbach´s
alpha). The results show that our key constructs can be represented by the items in the
survey.

@@

\text{red}{CONTINUE WITH THE OTHER KEY CONSTRUCTS – INPUT FROM TOMMY}

@@

To test our hypotheses, we run a sequential linear regression with heteroskedastic robust
standard errors and Heckmann two-step correction to control for attrition and survival
bias (ref). We test the mediation hypotheses within this framework using a causal
mediation \citep{Baron1986,MacKinnon2008} with quasi-Bayesian confidence intervals
over a million simulations \citep{Imai2010}. The sequential regression
model is presented chronologically in accordance with figure \ref{fig:fig1}. This entails that the
dependent variable in one model will be the independent in the next to study the evolution
of the proposed model sufficiently. The following models are estimated:

\par\noindent
\begin{align}
  OR_{2,i} &= \beta_0 + \beta_1 OR_{1,i} + \beta_2 DL_{i} + \mathbf{\Gamma C_i} + \epsilon_i\\
  OR_{2,i} &= \beta_0 + \beta_1 OR_{1,i} + \beta_2 DL_{i} + \beta_3 DC_{1,i} + \beta_4
               \Delta DC + \mathbf{\Gamma C_i} + \epsilon_i\\
  DC_{2,i} &= \gamma_0 + \gamma_1 DL_{1} + \gamma_2 DC_{1,i} + \mathbf{\Gamma C_i} + \upsilon_i\\
  CA_{2,i} &= \lambda_0 + \lambda_1 CA_{1,i} +
             \lambda_2 DC_{1,i} + \lambda_3 \Delta DC_i +\mathbf{\Gamma C_i}+ \mu_i \\
  CA_{2,i} &= \lambda_0 + \lambda_1 CA_{1,i} + \lambda_2 OR_{1,i} + \lambda_3 \Delta OR_i
             \lambda_4 DC_{1,i} + \lambda_5 \Delta DC_i +\mathbf{\Gamma C_i}+ \mu_i \\
  DL_{i} &= \xi_0 + \xi_1 DC_{1,i} +\mathbf{\Gamma C_i}+ \nu_i
\end{align}

Here $ \mathbf{\Gamma C_i}$ represents a vector of control variables including size, age,
dynamism, financial assets and profit margin. $\Delta DC_i$ is the change in $DC$ from
$T_1$ to $T_2$. Similarly $\Delta OR_i$ represents the change in $OR$.

In addition we estimate mediating models and test formally for mediation using the Baron
\& Kenny method \citep{Baron1986,MacKinnon2008}. We estimate two mediating model to test
if OR mediates the effect of DC on CA, and if DC mediates the effect of DL on OR,
respectively. The mediation equations for OR and DC respectively are state below:

\begin{align}
 \Delta DC_i &= \alpha_0 + \alpha_1 OR_{1,i} + \alpha_2 DL_{i} + \mathbf{\Gamma C_i} + u_i \\
 \Delta OR_i &= \omega_0 + \omega_1 CA_{1,i} + \omega_2 \Delta DC_{i} + \omega_3 CA_{1,i} + \mathbf{\Gamma C_i} + v_i
\end{align}

Finally, we run a Heckman selection model with selecting in to the sample at time $T_2$ is
determined by the following model:

\begin{align}
  P(R=1) &= \eta_0 + \eta_1 L_i + \eta_2 DC_{1,i} + \mathbf{\Gamma C_i} + m_i
\end{align}

$R$ is an indicator variable equal to 1 if the firm has responded at $T_2$ and 0 if
not. $L_i$ is an indicator set to 1 if the person answering the survey is the managing
director or CEO. This acts as an instrument for considering the probability of the firm
selection into the sample, but without having any theorized relationship with the main
outcome variables $DC$, $OR$, and $CA$. It is reasonable to assume that if the CEO was
involved in answering the survey at $T_1$, would increase the probability of the firm
answering at $T_2$ as well.

@@

\begin{table}[t]
\begin{singlespace}
  \caption{\small Descriptive statistics and correlations for variables in this paper}
  \label{tab:desc}

<<resultscorr, results="asis",echo=FALSE >>=

print(xtable(art2cor ,size="\\small",caption="Correlation matrix \\label{tab:cor}", align = c("l", rep("p{0.3in}",9)),table.placement="h", size = "\\small", tabular.environment="longtable"), size="scriptsize", label='tab:cor', caption.placement="top", floating=FALSE,latex.environments=NULL)

@
\vspace{1ex}

     \raggedright {\scriptsize Notes: Pairwise correlations between variables in the study
    excluding controls}
\end{singlespace}
\end{table}

\begin{table*}[t]
  \centering

\caption{Regression -How are MDC influencing evolution of lower level capabilities }

<<result1, results="asis", echo=FALSE >>=
stargazer(mainres,
          add.lines =list(c("Adjusted $R^2$",r1,r2,r3,r4,r5,r6)),
          single.row=FALSE, column.sep.width = "1pt", omit.stat=c("LL","ser","f","aic","rsq","adj.rsq"),
          no.space=FALSE,
          dep.var.labels=c("OR_{T_2}", "DC_{T_2}","CA_{T_2}","DL"),
        #  column.labels=c("HECKMAN","OLS","HECKMAN","OLS","HECKMAN","OLS"),
          model.names=FALSE,
          object.names=FALSE,

          ### order=c(1,3,2),

           ## covariate.labels= c("$OR_{T_1}$",
           ##                "$\\Delta OR$",
           ##                "$CA_{T_1}$"
           ##                "$DL$",
           ##                "$DC_{T_1}$",
           ##                "$\\Delta DC$",
           ##                "Firm size",
           ##                "Firm age",
           ##                "Environmental Dynamism",
           ##                "Firm profit margin",
           ##                "Firm assets"
           ##          ),

          title= "Regression results for model C", font.size="scriptsize",float=FALSE
          )

@
\label{tab:reg}
\end{table*}

\begin{figure}[t]

\begin{minipage}[t]{.5\textwidth}

  \resizebox{7cm}{!}{\input{./figure/medanalysis1.tex}}
  \captionof{figure}{Mediation analysis 1}
  \label{fig:fig3}
\end{minipage}%
\begin{minipage}[t]{.5\textwidth}
 \resizebox{7cm}{!}{\input{./figure/medanalysis2.tex}}
  \captionof{figure}{Mediation analysis 2}
  \label{fig:fig4}
\end{minipage}
\end{figure}

Table \ref{tab:reg} shows a summary of the regression models proposed in the previous
chapter. Models 1,2 and 3 are designed to test DL as \emph{antecedent} for $OR$ and
$DC$. Consider model 1 we observe that $DL$ is influencing the level of $OR$ within the
firm ($\beta_2 =$ \Sexpr{mod1_dl}) supporting H1. However, the effect disappears when we
add $DC$ in model 2 suggesting a mediating effect. In other words we see that firms with
initial high $DC$($\beta_3=$ \Sexpr{mod2_dc0}) and increasing $DC$ over time ($\beta_4=$
\Sexpr{mod2_ddc}) also have better $OR$. To control for the mediating effect suggested by
the change in coefficients for $DL$ between models 1 and 2, we performed a causal
mediation analysis as reported in figure \ref{fig:fig3}. This analysis confirms the
indications from models 1 and 2 showing that the direct effect from $DL$ on $OR$ is
insignificant and small (ADE = \Sexpr{medmod1_ade}). Meanwhile, the indirect effect
running through changes in $DC$ over time, is significant yielding a positive and
significant indirect effect of \Sexpr{medmod1_acme}. The proportion of the effect that is
mediated amounts to \Sexpr{medmod1_shmed}. In sum these results suggest that H1 is
unsupported, and that the bulk of the effect is indirect running through $DC$, in line with
the expectations in H3. Similarly, we see from model 3 that $DC$ is indeed influenced by $DL$
above and beyond its own evolutionary trajectory. This is in line with our expectations
and lend support to H4.

To evaluate H5 proposing a feedback effect from $DC$ to $DL$, we turn to model 6 in table
\ref{tab:reg}. Controlled for the usual firm level controls we find a positive effect
($\xi_1=$ \Sexpr{mod6_dc0}) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
suggesting that firms with more $DC$ is more likely to generate opportunities where it
becomes more prevalent that learning will need to take place. One interesting finding is
also that this effect environmental dynamism decreases firms level of $DL$. This is indeed
puzzling and we will look in to this in a post-hoc analysis.\todo{When adding interactions
  we see that high environmental dynamism in conjunction with DC is positive for DL
  meaning that DC will indeed work to make firms more aware of the benefits of DL when
  environments are changing} It is also worth noting that models 1,2 and 3 have positive
and significant $\rho$ from the Heckman selection model indicating that selection is
leading to biased estimates. By running a Heckman correction we avoid this potential
problem.

Models 4 and 5 in table \ref{tab:reg} deals with the \emph{outcome} of DC. H6a and H6b
both considers effects of $DC$ on the competitive advantage of the firm $CA$. $CA$ is
influenced by the level of $DC$ of the firm indicating that dynamic capabilities are a
source of competitive advantage in line with our expectations. Furthermore, considering
model 5 we see that $OR$ also has a significant positive effect on $CA$ indicating that
operating routines can also be a source of advantage for the firm. Moreover, the
coefficient of $\Delta DC$ decline from \Sexpr{mod4_ddc} to \Sexpr{mod5_ddc} when we add
$OR$. This suggests that some mediation is at work, i.e. that changes in $DC$ leads to
changes in changes in $OR$ leading to $CA$. This indirect path is in line with the
expectations from our hypotheses and as described in figure \ref{fig:fig2}. When formally
testing this mediation running a causal mediation analysis (see figure \ref{fig:fig4}), we
find added support that both a \emph{direct-} and an \emph{indirect} path exist to explain
the relationship between $DC$ and $CA$ (ADE = \Sexpr{medmod5_ade}, ACME =
\Sexpr{medmod5_acme}) and a total mediated share of \Sexpr{medmod5_shmed}.

@@

\begin{table}
     \footnotesize
  \centering
\input{./figure/hyptab.tex}}
\end{table}

@@

The objective of this article is to study the antecedents and outcomes of dynamic
capabilities, particularly the role of deliberate learning in shaping dynamic capabilities
over time. Learning is arguably an important determinant of firm success (ref arrow and
more), and the deliberate investment in learning to learning (i.e. deliberate learning)
has a long standing position as a theoretical antecedent of dynamic capabilities
\citep{Zollo2002a,Eriksson2014,Schilke2018}. Furthermore, the role of deliberate learning
in creating better operational routines is well established (ref), but it`s role in
generating competietive advantage for the firm, is less understood. Alas, the main
mechanism, the VRIO principle \citep{Barney1991a} is well known and still deemed highly
relevant relevant in understanding the source of competitive advantage of the firm
\citep{Priem2001}. Despite the prevalent and considerable citation of the
\cite{Zollo2002a} model, neither an empirical analysis of the model propositions, nor it`s
connection to outcomes such as competitive advantage has, to our knowledge, been
undertaken.

Our proposed extension of \cite{Zollo2002a} as depicted in figure \ref{fig:fig1}, taps
into the debate on the most important \emph{antecedents} and \emph{outcomes} of dynamic
capabilities \cite{Eriksson2014,Schilke2018}. Our results indicate that deliberate
learning is indeed an important antecedent of dynamic capabilities. Firms with stronger
capabilities for deliberate learning will develop higher levels of dynamic
capabilities. Thus the deliberate decision to invest in systems for learning will lead to
the evolution of better capacities to "purposefully create, extend, or modify its resource
base" \citep[p. ###]{Helfat2007}. Indeed, this also follows from Zollo \& Winter`s
definition where "a dynamic capability is a learned and stable pattern of collective
activity through which the organization systematically generates and modifies its
operating routines in pursuit of improved effectiveness" \citep[p
###]{Zollo2002a}.

The next step of figure \ref{fig:fig1} is to establish the link between deliberate
learning and the operational routines of the firm. These operating routines are what
\cite{Winter2003} calls "how we can earn a living now" (p. 992) or the technical fitness
of the firm \citep{Helfat2007}. Such operational routines are the product of learning
processes over time and should indeed be linked to deliberate learning of the firm as
proposed by \cite{Zollo2002a}. However, we find that this direct effect between deliberate
learning and operational capabilities disappear when we introduce dynamic capabilities into
the model. This suggest that dynamic capabilities are evolving as a response to deliberate
learning and, in turn, shaping operational capabilities in line with expectations of Zollo
\& Winter. In other words, we find support for an indirect link between deliberate
learning and operational routines, but no direct path.

This finding may come from the fact that learning works differently at different levels of
the capabilities hierarchy \citep{Collis1994}. Considering operational capabilities as
zero-order capabilities \citep{Winter2003,Schilke2014a} defined as more "geared towards
the operational functioning of the firm" \citep[p. 340]{Zollo2002a}, learning may be more
ad-hoc and less routinized as experiences are accumulated "on the fly" or through
"learning by doing" (ref) rather than deliberate and systematic. Indeed, learning by doing
is established as a robust result in the empirical literature on it`s link to operational
excellence (ref). When learning becomes deliberate and systematic through investments in
learning to learn capabilities, this would not automatically strengthen the short term
evolution of operational capabilities directly \citep{Arthur2005}. \todo{Need some more
  references here}. These findings would also lend support to the notion of higher-order
dynamic capabilities (capabilities to change dynamic capabilities)
\citep{Collis1994,Winter2003,Schilke2014a} and that deliberate learning could be
classified as such. In contrast, ad-hoc learning based on repetitive actions by employees
does not satisfy the requirements for a dynamic capability as the actions are less
strategic and purposeful.

An interesting finding is also that deliberate learning itself could be seen as a function
of dynamic capabilities. We argue that this stems from firms with high levels and
evolution of dynamic capabilities will take more advantage of adapting to change and hence
creating more opportunities for learning. This leads the firm to realize the need for
more deliberate approach to systematic learning. Particularly, this would lead to more
investments in systems for learning and, in turn, improvements in dynamic and operational
capabilities. For obvious reasons this is a tough causal claim to make and we have little
support for a causal argument. The insight will thus need considerably better data and
empirical analysis going forward. However, it has some support in the literature where
learning can be seen as an outcome as well as an antecedent to dynamic capabilities
\citep{Schilke2018}. \todo{maybe add someting about the interaction with dynamism}

@@

Our operational construst of $DC$ captures dynamic capabilities in
a broad, non-functional, sense (e.g. as a broad-purpose capability rather than one for
a particular purpose) \citep{Schilke2018}, and will hence capture a mind-set of the
organization rather than a narrow set of learned capabilites. This makes our conclusions
more general, albeit maybe less precise in predicting what investments in deliberate
learning would nmean for important capacities such as new product development and
innovation. 
 BLABLABLABLA

>>>>

\documentclass[review,fleqn]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[textsize=tiny,colorinlistoftodos]{todonotes}
\usepackage{subfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{filecontents}
\input{preamble.tex}
%%\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\setlength{\mathindent}{0pt} %% NB MAYBEREMOVE BEFORE SUBMISSION

%%%% TURN OFF PAGE NUMBER FOR INCLUSION IN THESIS
%\pagenumbering{gobble}
%%%%%%%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\title{Dynamic capabilities and competitive advantage}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

To test the relationships between dynamic capabilities and competitive advantage we need a
proper metric of both. We also benefit vastly from studying the same firms over time.  The
lack of h longitudinal studies to investigate dynamics over time and control for path
dependency of organizational routines has been noted as permanent limitation for moving
the DC literature forward empirically and theoretically \cite{Schilke2018}.

@@

All firms that registered R\&D activities during May to December 2005 were approached
totaling in all 1721 firms. A web-based questionnaire was developed containing the
measures of the key constructs of this paper. A link to the questionnaire was e-mailed to
the firms within a month after they registered R\&D activities. The initial mailing was
followed by two e-mail reminders. Of the firms approached, 1199 (70 \%) returned filled-in
questionnaires. The 1199 companies that filled out the questionnaire were contacted again
9 years later. The majority of firms were contacted in spring/summer 2014. All received a
web-based questionnaire containing the same measures of the focal constructs of this
paper. 283 of the firms returned filled-in questionnaire.

@@

@@

The focal constructs of this paper are dynamic capabilities, operational routines and
competitive advantage. These are all operationalized using the survey data described
above. Table 1 below describes the items used to operationalize the focal constructs and
their internal validity in forming an additive index (Cronbach´s alpha). The results show
that our key constructs can be represented by the items in the survey.

@@

@@

To test our hypotheses, we run a sequential linear regression with heteroskedastic robust
standard errors. We test the mediation hypotheses within this framework using a causal
mediation \citep{Baron1986,MacKinnon2008} with quasi-Bayesian confidence intervals and
over a million simulations \citep{Imai2010}.

In addition we estimate mediating models and test formally for mediation using the Baron
\& Kenny method \citep{Baron1986,MacKinnon2008}. We estimate two mediating model to test
if OR mediates the effect of DC on CA, and if DC mediates the effect of DL on OR,
respectively.

@@

Table \ref{tab:reg} shows a summary of the regression models proposed in the previous
chapter. Models 1,2 and 3 are designed to test DL as \emph{antecedent} for $OR$ and
$DC$. Consider model 1 we observe that $DL$ is influencing the level of $OR$ within the
firm ($\beta_2 =$ 0.325) supporting H1. However, the effect disappears when we
add $DC$ in model 2 suggesting a mediating effect. In other words we see that firms with
initial high $DC$($\beta_3=$ -0.007) and increasing $DC$ over time ($\beta_4=$
0.497) also have better $OR$. To control for the mediating effect suggested by
the change in coefficients for $DL$ between models 1 and 2, we performed a causal
mediation analysis as reported in figure \ref{fig:fig3}. This analysis confirms the
indications from models 1 and 2 showing that the direct effect from $DL$ on $OR$ is
insignificant and small (ADE = 0.05). Meanwhile, the indirect effect
running through changes in $DC$ over time, is significant yielding a positive and
significant indirect effect of 0.222. The proportion of the effect that is
mediated amounts to 0.818. In sum these results suggest that H1 is
unsupported, and that the bulk of the effect is indirect running through $DC$, in line with
the expectations in H3. Similarly, we see from model 3 that $DC$ is indeed influenced by $DL$
above and beyond its own evolutionary trajectory. This is in line with our expectations
and lend support to H4.

To evaluate H5 proposing a feedback effect from $DC$ to $DL$, we turn to model 6 in table
\ref{tab:reg}. Controlled for the usual firm level controls we find a positive effect
($\xi_1=$ 0.913) from $DC_{T_1}$ on $DL$ measured at $T_1$. This supports H5
suggesting that firms with more $DC$ is more likely to generate opportunities where it
becomes more prevalent that learning will need to take place. One interesting finding is
also that this effect environmental dynamism decreases firms level of $DL$. This is indeed
puzzling and we will look in to this in a post-hoc analysis.\todo{When adding interactions
  we see that high environmental dynamism in conjunction with DC is positive for DL
  meaning that DC will indeed work to make firms more aware of the benefits of DL when
  environments are changing} It is also worth noting that models 1,2 and 3 have positive
and significant $\rho$ from the Heckman selection model indicating that selection is
leading to biased estimates. By running a Heckman correction we avoid this potential
problem.

Models 4 and 5 in table \ref{tab:reg} deals with the \emph{outcome} of DC. H6a and H6b
both considers effects of $DC$ on the competitive advantage of the firm $CA$. $CA$ is
influenced by the level of $DC$ of the firm indicating that dynamic capabilities are a
source of competitive advantage in line with our expectations. Furthermore, considering
model 5 we see that $OR$ also has a significant positive effect on $CA$ indicating that
operating routines can also be a source of advantage for the firm. Moreover, the
coefficient of $\Delta DC$ decline from 0.589 to 0.425 when we add
$OR$. This suggests that some mediation is at work, i.e. that changes in $DC$ leads to
changes in changes in $OR$ leading to $CA$. This indirect path is in line with the
expectations from our hypotheses and as described in figure \ref{fig:fig2}. When formally
testing this mediation running a causal mediation analysis (see figure \ref{fig:fig4}), we
find added support that both a \emph{direct-} and an \emph{indirect} path exist to explain
the relationship between $DC$ and $CA$ (ADE = 0.371, ACME =
0.198) and a total mediated share of 0.347.

@@

@@

@@
